### 2021-08-06 papers/modeling-of-combined-lfr-csp-sco2-paper/content.tex
new updates to methods and materials

\section{Introduction}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Materials and Methods}

@@

\subsection{Cycle Component Modeling}
\subsubsection{Counter Flow and Black Box Heat Exchangers}

\subsubsection{Turbines}

\subsubsection{Compressors}

\subsubsection{Lead-Fast Reactor}

\subsubsection{Concentrating Solar Power Cycle}

The CSP cycles modeled in this paper are composed of the hot and cold thermal energy storage, pumps to move the molten salt, and a black box heat input. The diagram for this CSP cycle is seen in Figure \ref{csp}.

@@

The salt CSP cycle can be either in charging mode or electrical generation mode. 
%Here you need to explain what a conventional CSP cycle looks like (briefly). I.e. CSP charges salt, it can discharge when you want it to. Now with our configuration we introduce a 'new' charging mode where heat comes in from the SALT HX as well as from the sun, via the sCO2 Brayton as you say
When the CSP cycle is in charging mode, excess heat is transfered from the sCO$_{2}$ Brayton cycle through the SALT HX. The heated salt is then stored in the hot storage until grid demand increases.   
%Explain why there is no charging and discharging at same time - because if there is electricity demand heat from LFR would be dispatched direclty rather than thru the SALT HX

When electrical generation is occuring, the heat input in this cycle is modelled through a black box energy balance across states S6-A and S1-A with a heat addition of 7.5e8 W from the heliostat field. The hot storage is moved through Pump 3 and transfers heat into the sCO$_{2}$ Brayton cycle to be converted into electricity. The cooled salt is stored in cold storage and moved through Pump 2 where the heat addition from the heliostat field is added.

\subsection{Generalization of Cycle Modeling}

The cycles presented are generalized in order to draw a more direct comparison. The generalized parameters include isentropic efficiencies, heat exchanger approach temperatures, pressures, heat input, and pump constants. These values are summarized in Table \ref{cycle-constants}.

\begin{specialtable}[H] 
    \caption{Constant cycle parameters with definition, variable and set value. \label{cycle-constants}}
    \begin{tabular}{lcc}
    \toprule
    \textbf{Parameter} & \textbf{Variable}	& \textbf{Design Point Value}\\
    \midrule
    \textit{Efficiencies}\\
    Main Compressor & $\eta_{MC}$		& 0.91 (-)\\
    Re-Compressor & $\eta_{RC}$		& 0.89 (-)\\
    Turbine & $\eta_{T}$		& 0.90 (-)\\
    Pump & $\eta_{P}$      & 0.90 (-)\\
    \midrule
    \textit{Approach Temperatures}\\
    Low Temperature Recuperator & $\delta_{LTR}$		& 10 (K)\\
    High Temperature Recuperator & $\delta_{HTR}$		& 10 (K)\\
    Concentrating Solar Power Heat Exchanger & $\delta_{CSPHX}$	& 10 (K)\\
    \midrule
    \textit{Pressures}\\
    Pressure Ratio & $PR$ & 3.27 (-)\\
    High Side Pressure & $P_{2A}$ & 2.88e7 (Pa)\\
    \midrule
    \textit{Heat Into System}\\
    Lead-Fast Reactor Heat Transfer & $\dot{Q}_{LFRHX}$ & 9.5e8 (W)\\
    Concentrating Solar Power Heat Transfer & $\dot{Q}_{CSP}$ & 7.5e8 (W)\\
    \midrule
    \textit{Temperature}\\
    Main Compressor Inlet & $T_{1A}$ & 313.2 (K)\\
    %Lead-Fast Reactor sCO$_{2}$ Low Temperature & $T_{4}$,$T_{1C}$,$T_{5A}$,$T_{4C}$ & 673.2 (K)\\
    Lead-Fast Reactor sCO$_{2}$ High Temperature & $T_{5}$,$T_{2C}$,$T_{6A}$,$T_{5C}$ & 868.2 (K)\\
    \midrule
    \textit{Pumps}\\
    Pressure Rise Across Pump & $\Delta_{P}$ & 3.726e6 (Pa)\\
    Pump Low Side Pressure & $P_{S5-B}$ & 3.0e6 (Pa)\\ 
    \bottomrule
    \end{tabular}
\end{specialtable}

The values displayed in Table \ref{cycle-constants} are representative of LFR and CSP design while being consistent with design parameters given by our industry partner, Westinghouse Electric Company.

@@

\subsection{Non-Charging Cycle Configurations}%===================================
Various cycles are modeled to test their advantages and disadvantages. These cycle models fall into two categories: non-charging and charging. The non-charging category is used to determine the configuration of the cycle with a focus on electricity generation. This includes the number and location of turbines, recuperators, and heat input to the system by the CSP and LFR. To quantify the effectiveness of the non-charging configurations, a cycle efficiency, $\eta_{cycle}$, is defined in Equation \ref{eq-eta-cycle}.

\begin{equation}
    \label{eq-eta-cycle}
    \eta_{heatstorage} = \frac{\dot{W}_{T}-\dot{W}_{MC}-\dot{W}_{RC}}{\dot{Q}_{LFRHX}+\dot{Q}_{CSPHX}},
\end{equation}

The numerator in Equation \ref{eq-eta-cycle} is the Alternator power, or the power produced from the turbines, $\dot{W}_{T}$, minus the required power of the compressors, $\dot{W}_{MC}$ and $\dot{W}_{RC}$. The denominator is the total power input into the system from the LFR, $\dot{Q}_{LFRHX}$, and CSP, $\dot{Q}_{CSPHX}$.

%BL: I would include the naming scheme upfront and give a table (C-LFR-ON etc.)

\subsubsection{Two-Cycle Configuration: C-LFR-ON and C-CSP-ON} %--------------------------------------------------------

The two-cycle configuration that is tested has independent sCO$_{2}$ loops bridged by a salt CSP cycle. This cycle has two sCO$_{2}$ Brayton Cycles: C-LFR-ON and C-CSP-ON. Configuration of components for these two cycles is identical with the exception of heat inputs. C-LFR-ON has heat provided from a LFR while C-CSP-ON has heat provided from a CSP. These two cycles individually operate when the focus of plant operation is primarily electricity generation.

The LFR cycle for this two-cycle configuration is labeled as C-LFR-ON and the cycle diagram is illustrated in Figure \ref{c-lfr-on}.

@@

Two seperate sensitivity studies on the LFR inlet temperature are completed for C-LFR-ON. The unconstrained study is performed by gradually increasing the mass flow to the main compressor while maximizing cycle efficiency. The constrained study is calculated by setting the LFR inlet temperature to the design value of 673.2 K (400^${circ}C), which is a requirement of the LFR primary circuit to maximize power output within material limits.
%BL: flip the order of this para: constrained then unconstrained. State that the unconstrained is a 'sensitivty' case to determine the penalty of the constraint

The CSP cycle for this two-cycle configuration is labeled C-CSP-ON and the cycle diagram is shown in Figure \ref{c-csp-on}. The diagram has the necessary pumps, TES tanks, and salt heat exchangers to be representative of a relizable salt CSP cycle.

@@

\subsubsection{C-1HTR1T-ON} %-----------------------------------------------------

One drawback of having a two-cycle design, as seen in the C-LFR-ON and C-CSP-ON, is doubling the number of system components. Combining the two cycles into one would reduce redundancy and complexity. Heat addition from the CSP and LFR in parallel orientation is therefore studied in the C-1HTR1T-ON model. This model studies what impact mixing different temperature flows prior to the turbine has on cycle efficiency. The diagram for this cycle is illustrated in Figure \ref{c-1htr1t-on}.

@@

In this cycle, the LFR and CSP have identical inlet temperatures due to splitting the flow prior to their parallel orientation. Therefore, three sensitivity studies are done on the C-1HTR1T-ON EES model. The initial two studies have the low LFR temperature constrained to the value of 673.2 K with varied cold CSP TES and maximized cycle efficiency. The two tested values for cold CSP TES with constrained LFR low temperature are 683.2 K and 713.2 K. The desired cold CSP TES temperature of 663.2 K is not possible with the constraint on the LFR low temperature (because it cannot be colder than the sCO$_2$ that removes heat from the salt). In this case, to obtain the desired cold CSP TES temperature, the constraint on the LFR low temperature is removed, droping the temperature of the LFR inlet to 653.2 K. 
%BL: I think I understand what you're talking about but the above para could spell out all the sensitivity cases a bit more clearly, perhaps as bullets. Asp you will want to explain the criteria that go into cold storage temp. Lower = more delta T = more dispatchability

\subsubsection{C-2HTR3T-ON} %-----------------------------------------------------

@@

\subsection{Thermal Energy Storage Charging Techniques} %=========================

Charging cycle configurations focus on an energy storage operating mode. These configurations test the optimal location of LFR heat extraction through the SALT HX. To maximize the available heat for extraction, alternator power is set to zero and turbine power is therefore equal to the compressors' demand. The excess energy from the LFR is thermally stored in the TES for later use when grid demand increases. Comparison of where thermal energy is extracted in the cycle is done by using the same Brayton cycle, C-LFR-ON, and configuring the salt heat exchanger in different locations around the turbine. To quantify the effectiveness of TES charging techniques a heat storage efficiency, $\eta_{heatstorage}$, is defined by Equation \ref{eq-eta-heatstorage}.
%BL: explain that as a (re)compression cycle is still being run for the LFR and the components are not perfectly efficient, it will consume power moving the fluid around that needs to be balanced with some of the thermal output
%BL: SALT HX could perhaps be better named sCO2-to-Salt or C2S for short perhaps! Np if you dont want to change it at this late stage

\begin{equation}
    \label{eq-eta-heatstorage}
    \eta_{heatstorage} = \frac{\dot{Q}_{SALT}}{\dot{Q}_{LFRHX}+\dot{Q}_{CSPHX}},
\end{equation}

Whereas $\dot{Q}_{SALT}$ is the amount of heat transfered through the SALT HX and the addition of $\dot{Q}_{LFRHX}$ and $\dot{Q}_{CSPHX}$ is the total amount of heat input into the system from the LFR and CSP.

\subsubsection{C-LFR-PRE} %-------------------------------------------------------

@@

\subsubsection{C-LFR-POST} %------------------------------------------------------

@@

\subsubsection{C-LFR-PAR} %-------------------------------------------------------

@@

\subsubsection{C-LFR-CIRC} %------------------------------------------------------

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}

\subsection{Non-Charging Cycle Configurations}

\subsubsection{C-LFR-ON and C-CSP-ON}

@@

\begin{specialtable}[H] 
    \caption{Calculated system parameters for non-charging C-LFR-ON cycle configuration with constrained (\textit{C}) and unconstrained (\textit{U}) Lead-Fast Reactor low-end temperature.\label{tab-c-lfr-on}}
    \begin{tabular}{lccc}
    \toprule
    \textbf{Definition} & \textbf{Variable} & \textit{U} & \textit{C}\\
    \midrule
    LFR Inlet Temperature (K)	&	$T_{4}$	&	Data	&	Data	\\
    Cycle Efficiency (\%)	&	$\eta_{cycle}$	&	Data	&	Data	\\
    Alternator Power (W)	&	$\dot{W}_{A}$	&	Data	&	Data	\\
    PC Heat Transfer	&	$\dot{Q}_{PC}$	&	Data	&	Data	\\
    MC Power (W)	&	$\dot{W}_{MC}$	&	Data	&	Data	\\
    RC Power (W)	&	$\dot{W}_{RC}$	&	Data	&	Data	\\
    Turbine Power (W)	&	$\dot{W}_{T}$	&	Data	&	Data	\\
    MC Mass Flow Fraction (-)	&	$y_{1}$	&	Data	&	Data	\\
    LTR UA Value (W/K)	&	$UA_{LTR}$	&	Data	&	Data	\\
    LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	Data	&	Data	\\
    LTR Heat Transfer Rate (W)	&	$\dot{Q}_{LTR}$	&	Data	&	Data	\\
    LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	Data	&	Data	\\
    HTR UA Value (W/K)	&	$UA_{HTR}$	&	Data	&	Data	\\
    HTR Capacitance Ratio (-)	&	$CR_{HTR}$	&	Data	&	Data	\\
    HTR Heat Transfer Rate (W)	&	$\dot{Q}_{HTR}$	&	Data	&	Data	\\
    HTR Effectiveness (-)	&	$\varepsilon_{HTR}$	&	Data	&	Data	\\
    \bottomrule
    \end{tabular}\\
\end{specialtable}

@@

\subsubsection{C-1HTR1T-ON}

@@

\subsubsection{C-2HTR3T-ON}

@@

\subsection{Thermal Energy Storage Charging Techniques}

\subsubsection{C-LFR-PRE}

@@

\subsubsection{C-LFR-POST}

\subsubsection{C-LFR-PAR}

@@

\subsubsection{C-LFR-CIRC}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{how to use}

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Materials and Methods}

@@

\subsection{Cycle Component Modeling}
%======================================================================================
Components present in the cycles are modeled using various techniques. Turbines and compressors are analyzed using isentropic efficiencies. Counter flow heat exchangers use the effectiveness-NTU method while black box heat exchangers use a simple energy balance for state point calculations. The lead-cooled fast reactor is assumed to be a black box heat exchanger because of the constant heat input and state points on the sCO$_2$ inlet and outlet are provided. The concentrating solar power cycle is modeled with necessary components including hot and cold TES, reciever, pumps and counter flow heat exchangers.

\subsubsection{Turbines and Compressors }
%--------------------------------------------------------------------------------------

The modeled cycles have a number of compressors and turbines. The turbines and compressors are modeled for each cycle using constant isentropic efficiency values summarized in Table \ref{tab-cycle-constants}. Turbines take the high pressure sCO$_2$ and expand it through a series of blades allowing a production of energy, while compressors input mechanical energy to increase the pressure of the sCO$_2$. The turbines and compressors are assumed to be at steady state, exchange no heat with the surroundings, and have a single inlet and outlet. Power calculations are initially done on ideal, reversible compressors or turbines then are scaled by the isentropic efficiencies to provide an estimate for a realizable component. Using this estimate, along with a known low and high side pressures, temperature and enthalpy outlets of the turbine and compressor can be calculated \cite{klein_nellis_2011}.

\subsubsection{Black Box and Counter Flow Heat Exchangers}
%--------------------------------------------------------------------------------------

Black box heat exchangers are simplified heat exchangers which have no approach temperature or pinch point. These heat exchangers use an energy balance with mass flow inlet energy, heat input or output, and mass flow outlet energy. The energy balance equation used for all black box heat exchangers is Equation \ref{eq-black}.

\begin{equation}
    \label{eq-black}
    \dot{m}_{in}*h_{in} + \dot{Q}_{in} = \dot{m}_{out}*h_{out} + \dot{Q}_{out},
\end{equation}

In this equation the energy input to the system is on the left hand side with $\dot{m}_{in}$ multiplied by $h_{in}$ being energy from the mass flow and $\dot{Q}_{in}$ being heat transfer directly to the flow from an outside source. The right hand side of the equation is heat leaving the energy balance. The mass flow leaving is $\dot{m}_{out}$ with enthalpy of $h_{out}$ and $\dot{Q}_{out}$ is the heat transfer leaving from the flow. Black box energy balances are used in three situations, the Reciever, LFR HX, and PC HX. These heat exchangers are not exchaustively modeled because the state points on the inlet and outlet are constrained by design parameters.

Counter flow heat exchangers are modeled with two fluids flowing in opposite directions exchanging heat from the hot side to the cold side. The temperatures of the hot and cold flows on either side of the the heat exchanger have a temperature difference known as an approach temperature. A diagram showing a simplified example of a counterflow heat exchanger is illustrated in Figure \ref{counter-flow-hx}.

\end{paracol}
\begin{figure}[H] 
    \widefigure
    \includegraphics[width=10 cm]{Definitions/counter-flow-hx.pdf}
    \caption{Simple counter flow heat exchanger diagram. \label{counter-flow-hx}}
\end{figure}
\begin{paracol}{2}
\linenumbers
\switchcolumn

Additional assumptions of the counter flow heat exchanger model are no heat loss to the surroundings, $\dot{Q}_{surr}$ is zero, and no pressure drops accross the heat exchangers. Counter flow heat exchanger calculations require two known state points, fluid libraries, mass flow rate of hot and cold side, and a specified approach temperature. In all of the modeled cases, the approach temperature is set to a value of 10 K. The fluid libraries referenced are built into EES for Carbon Dioxide and Salt(60\% NaNO3 40\% KNO3) \cite{pacheco_1995_salt_properties,roland_1996_co2_properties}.

To analyze the counter flow heat exchanger a side is chosen, usually high, to start the calculations. The approach temperature is initially subtracted from the hot stream on the high side to find the missing cold temperature according to Equation \ref{temp_h}.

\begin{equation}
   \label{temp_h}
    T_{out,c} = T_{in,h}-\Delta_{T},
\end{equation}

Where T$_{out,c}$ is the cold stream outlet temperature and T$_{in,h}$ is the hot stream inlet temperature. Knowing the two state points allows for the enthalpy to be found using correlations from the fluid property libraries.

[More Desctription on Counterflow HX]

\subsubsection{Lead-Cooled Fast Reactor}
%--------------------------------------------------------------------------------------
Lead-cooled fast reactors use energy from a controlled nuclear reaction to heat molten lead. This lead is used to both cool the core as well as transfer heat into the sCO$_2$ Brayton power cycle \cite{smith_2016_lfr_background,alemberti_2013_lfr_overview}. The lead-cooled fast reactor is assumed to be a black box heat transfer and is labeled in the cycle models LFR HX. The inlet, outlet and heat transfer rates are defined by our industry partner, Westinghouse Electric Company making the black box simplification viable. The energy balance for the black box assumption can be seen in Equation \ref{eq-lfr-black-box}.

\begin{equation}
    \label{eq-lfr-black-box}
    \dot{m}_{inlet}*h_{inlet} + \dot{Q}_{LFRHX} = \dot{m}_{outlet}*h_{outlet},
\end{equation}

Where the left hand side, $\dot{m}_{inlet}$, $h_{inlet}$, and $\dot{Q}_{LFRHX}$, is the energy into the flow and the right hand side, $\dot{m}_{outlet}$ and $h_{outlet}$, is the energy brought out from the flow of sCO$_2$. The amount of energy transfered into the cycle, $\dot{Q}_{LFRHX}$, is set at 950 MW, and outlet temperature of the sCO$_2$ from the LFR HX is set at a value of 595$^{\circ}$C. The outlet temperature of the LFR is rigid due to high temperature material limits on the LFR lead side. Low sCO$_2$ LFR inlet temperature has a lower limit of 340$^{\circ}$C and an optimal value of 400$^{\circ}$C. Increasing this temperature above this optimal value leads to diminishing returns on the LFR efficiency.

\subsubsection{Concentrating Solar Power Cycle}
%--------------------------------------------------------------------------------------

The CSP salt cycle modeled in this paper is composed of hot and cold thermal energy storage (TES), pumps, receiver, sCO$_2$-to-Salt counter flow heat exchanger (C2S), and CSP counter flow heat exchanger (CSP HX). The diagram for this CSP salt cycle is seen in Figure \ref{csp}.

@@

The CSP salt cycle uses 60\% sodium nitrate and 40\% potassium nitrate 'solar salt' as the heat transfer fluid. Solar salt stored in the hot TES can be dispatched on demand through the CSP HX when grid demand increases and held when grid demand is low. Current CSP salt cycles heat solar salt with receivers and store it in hot TES tanks at 565$^{\circ}$C. Future CSP salt cycles are hypothesized to have bulk hot TES temperatures of up to 720$^{\circ}$C, but due to high temperature limitations with the LFR outlet, the hot TES temperature is set at 595$^{\circ}$C for all modeled cycles \cite{mehos2017concentrating}. The cold TES temperature takes on three different values according to cycle configuration capabilitites: 390$^{\circ}$C, 410$^{\circ}$C, and 440$^{\circ}$C. In addition to the lower hot TES temperature, current CSP salt cycles lack a secondary option for charging the hot TES \cite{hamilton2020dispatch}. The studied CSP salt cycle has two TES charging options: a receiver, which generates heat from a heliostat field, and C2S heat exchanger, which draws excess heat from the sCO$_2$ Brayton cycle. It is assumed that only one hot TES charging option can be active at any given time.

The C2S heat exchanger is active during the 'charging' cycle configurations, when the focus is on heat storage for later use. During this process there is no solar salt flow through the receiver. Pump 1 is active moving solar salt from cold TES to hot TES through the C2S heat exchanger, which is extracting heat from the sCO$_2$ Brayton cycle.

'Non-charging' cycle configurations has the receiver charging the hot TES, C2S heat exchanger is not transfering heat, and the LFR is dispatching energy directly into electrical generation. When electrical generation is occuring, the heat input in this cycle is modelled through a black box energy balance across states S6-A and S1-A with a heat addition of 7.5e8 W from the heliostat field. The hot storage is moved through Pump 3 and transfers heat into the sCO$_{2}$ Brayton cycle to be converted into electricity. The cooled salt is stored in cold storage and moved through Pump 2 where the heat addition from the receiver is added.

\subsection{Generalization of Cycle Modeling}
%======================================================================================

The cycles presented are generalized in order to draw a more direct comparison. The generalized parameters include isentropic efficiencies, heat exchanger approach temperatures, pressures, heat input, and pump constants. These values are summarized in Table \ref{tab-cycle-constants}.

\begin{specialtable}[H] 
    \caption{Constant cycle parameters with definition, variable and set value. \label{tab-cycle-constants}}
    \begin{tabular}{lcc}
    \toprule
    \textbf{Parameter} & \textbf{Variable}	& \textbf{Design Point Value}\\
    \midrule
    \textit{Efficiencies}\\
    Main Compressor & $\eta_{MC}$		& 0.91 (-)\\
    Re-Compressor & $\eta_{RC}$		& 0.89 (-)\\
    Turbine & $\eta_{T}$		& 0.90 (-)\\
    Pump & $\eta_{P}$      & 0.90 (-)\\
    \midrule
    \textit{Approach Temperatures}\\
    Low Temperature Recuperator & $\delta_{LTR}$		& 10 (K)\\
    High Temperature Recuperator & $\delta_{HTR}$		& 10 (K)\\
    Concentrating Solar Power Heat Exchanger & $\delta_{CSPHX}$	& 10 (K)\\
    \midrule
    \textit{Pressures}\\
    Pressure Ratio & $PR$ & 3.27 (-)\\
    High Side Pressure & $P_{2A}$ & 2.88e7 (Pa)\\
    \midrule
    \textit{Heat Into System}\\
    Lead-Cooled Fast Reactor Heat Transfer & $\dot{Q}_{LFRHX}$ & 9.5e8 (W)\\
    Concentrating Solar Power Heat Transfer & $\dot{Q}_{CSP}$ & 7.5e8 (W)\\
    \midrule
    \textit{Temperature}\\
    Main Compressor Inlet & $T_{1A}$ & 313.2 (K)\\
    %Lead-Cooled Fast Reactor sCO$_{2}$ Low Temperature & $T_{4}$,$T_{1C}$,$T_{5A}$,$T_{4C}$ & 673.2 (K)\\
    Lead-Cooled Fast Reactor sCO$_{2}$ High Temperature & $T_{5}$,$T_{2C}$,$T_{6A}$,$T_{5C}$ & 868.2 (K)\\
    \midrule
    \textit{Pumps}\\
    Pressure Rise Across Pump & $\Delta_{P}$ & 3.726e6 (Pa)\\
    Pump Low Side Pressure & $P_{S5-B}$ & 3.0e6 (Pa)\\ 
    \bottomrule
    \end{tabular}
\end{specialtable}

The values displayed in Table \ref{tab-cycle-constants} are representative of LFR and CSP design while being consistent with design parameters given by our industry partner, Westinghouse Electric Company.

@@

Modeled cycles are summarized in Table \ref{tab-cycle_sum}.

\begin{specialtable}[H] 
    \caption{Summary of all modeled non-charging and charging cycles with descriptions. \label{tab-cycle_sum}}
    \begin{tabular}{ll}
    \toprule
    \textbf{Cycle Label} & \textbf{Description}\\
    \midrule
    \textit{Non-Charging}\\
    C-LFR-ON & Two-cycle configuration with LFR as heat source.\\
    C-CSP-ON & Two-cycle configuration with CSP as heat source.\\
    C-1HTR1T-ON & CSP and LFR heat sources in parallel with one turbine.\\
    C-2HTR3T-ON & Seperatre CSP and LFR loops each with dedicated HTR and turbine.\\
    \midrule
    \textit{Charging}\\
    C-LFR-PRE & Turbine is prior to the SALT HX.\\
    C-LFR-POST & Turbine is after the SALT HX.\\
    C-LFR-PAR & Turbine is parallel to the SALT HX.\\
    C-LFR-CIRC & Circulator bridges the LFR and SALT HX.\\
    \bottomrule
    \end{tabular}
\end{specialtable}

\subsection{Non-Charging Cycle Configurations} 
%======================================================================================

Various cycles are modeled to test their advantages and disadvantages. These cycle models fall into two categories: non-charging and charging. The non-charging category is used to determine the configuration of the cycle with a focus on electricity generation. This includes the number and location of turbines, recuperators, and heat input to the system by the CSP and LFR. To quantify the effectiveness of the non-charging configurations, a cycle efficiency, $\eta_{cycle}$, is defined in Equation \ref{eq-eta-cycle}.

\begin{equation}
    \label{eq-eta-cycle}
    \eta_{cycle} = \frac{\dot{W}_{T}-\dot{W}_{MC}-\dot{W}_{RC}}{\dot{Q}_{LFRHX}+\dot{Q}_{CSPHX}},
\end{equation}

The numerator in Equation \ref{eq-eta-cycle} is the Alternator power, or the power produced from the turbines, $\dot{W}_{T}$, minus the required power of the compressors, $\dot{W}_{MC}$ and $\dot{W}_{RC}$. The denominator is the total power input into the system from the LFR HX, $\dot{Q}_{LFRHX}$, and CSP HX, $\dot{Q}_{CSPHX}$.

\subsubsection{Two-Cycle Configuration: C-LFR-ON and C-CSP-ON} %--------------------------------------------------------------------------------------

The two-cycle configuration that is tested has independent sCO$_{2}$ loops bridged by a CSP cycle. This cycle has two sCO$_{2}$ Brayton Cycles: C-LFR-ON and C-CSP-ON. Configuration of components for these two cycles is identical with the exception of heat inputs. C-LFR-ON has heat provided from a LFR while C-CSP-ON has heat provided from the CSP. These two cycles individually operate when the focus of plant operation is primarily electricity generation.

The cycle that is using the LFR heat input in the two-cycle configuration is labeled as C-LFR-ON and the cycle diagram is illustrated in Figure \ref{c-lfr-on}.

@@

Two seperate sensitivity studies on the LFR inlet temperature are completed for C-LFR-ON. The unconstrained study is performed by gradually increasing the mass flow to the main compressor while maximizing cycle efficiency. The constrained study is calculated by setting the LFR inlet temperature to the design value of 673.2 K (400$^{\circ}$C), which is a requirement of the LFR primary circuit to maximize power output within material limits.
%BL: flip the order of this para: constrained then unconstrained. State that the unconstrained is a 'sensitivty' case to determine the penalty of the constraint

The cycle that is using the CSP heat input in the two-cycle configuration is labeled C-CSP-ON and the cycle diagram is shown in Figure \ref{c-csp-on}.

@@

\subsubsection{C-1HTR1T-ON} 
%--------------------------------------------------------------------------------------

One drawback of having a two-cycle design, as seen in the C-LFR-ON and C-CSP-ON, is doubling the number of system components. Combining the two cycles into one would reduce redundancy and complexity. Heat addition from the CSP HX and LFR HX in parallel orientation is therefore studied in the C-1HTR1T-ON model. This model studies what impact mixing different temperature flows prior to the turbine has on cycle efficiency. The diagram for this cycle is illustrated in Figure \ref{c-1htr1t-on}.

@@

In this cycle, the LFR HX and CSP HX have identical inlet temperatures due to splitting the flow prior to their parallel orientation. Therefore, three sensitivity studies are done on the C-1HTR1T-ON EES model. The initial two studies have the low LFR temperature constrained to the value of 673.2 K with varied cold CSP TES and maximized cycle efficiency. The two tested values for cold CSP TES with constrained LFR low temperature are 683.2 K and 713.2 K. The desired cold CSP TES temperature of 663.2 K is not possible with the constraint on the LFR low temperature (because it cannot be colder than the sCO$_2$ that removes heat from the salt). In this case, to obtain the desired cold CSP TES temperature, the constraint on the LFR low temperature is removed, droping the temperature of the LFR inlet to 653.2 K. 
%BL: I think I understand what you're talking about but the above para could spell out all the sensitivity cases a bit more clearly, perhaps as bullets. Asp you will want to explain the criteria that go into cold storage temp. Lower = more delta T = more dispatchability

\subsubsection{C-2HTR3T-ON} 
%--------------------------------------------------------------------------------------

@@

\subsection{Thermal Energy Storage Charging Techniques} 
%======================================================================================

Charging cycle configurations focus on an energy storage operating mode. These configurations test the optimal location of LFR heat extraction through the SALT HX. To maximize the available heat for extraction, alternator power is set to zero and turbine power is therefore equal to the compressors' demand. The excess energy from the LFR is thermally stored in the TES for later use when grid demand increases. Comparison of where thermal energy is extracted in the cycle is done by using the same Brayton cycle, C-LFR-ON, and configuring the salt heat exchanger in different locations around the turbine. To quantify the effectiveness of TES charging techniques a heat storage efficiency, $\eta_{heatstorage}$, is defined by Equation \ref{eq-eta-heatstorage}.
%BL: explain that as a (re)compression cycle is still being run for the LFR and the components are not perfectly efficient, it will consume power moving the fluid around that needs to be balanced with some of the thermal output

\begin{equation}
    \label{eq-eta-heatstorage}
    \eta_{heatstorage} = \frac{\dot{Q}_{C2S}}{\dot{Q}_{LFRHX}+\dot{Q}_{CSPHX}},
\end{equation}

Whereas $\dot{Q}_{S2C}$ is the amount of heat transfered through S2C and the addition of $\dot{Q}_{LFRHX}$ and $\dot{Q}_{CSPHX}$ is the total amount of heat input into the system from the LFR HX and CSP HX.

\subsubsection{C-LFR-PRE} 
%--------------------------------------------------------------------------------------

@@

\subsubsection{C-LFR-POST} 
%--------------------------------------------------------------------------------------

@@

\subsubsection{C-LFR-PAR} 
%--------------------------------------------------------------------------------------

@@

\subsubsection{C-LFR-CIRC} 
%--------------------------------------------------------------------------------------

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}

\subsection{Non-Charging Cycle Configurations}
%======================================================================================

\subsubsection{C-LFR-ON and C-CSP-ON}
%--------------------------------------------------------------------------------------

@@

\begin{specialtable}[H] 
    \caption{Calculated system parameters for non-charging C-LFR-ON cycle configuration with constrained (\textit{C}) and unconstrained (\textit{U}) lead-cooled fast reactor low-end temperature.\label{tab-c-lfr-on}}
    \begin{tabular}{lccc}
    \toprule
    \textbf{Definition} & \textbf{Variable} & \textit{U} & \textit{C}\\
    \midrule
    LFR Inlet Temperature (K)	&	$T_{4}$	&	Data	&	Data	\\
    Cycle Efficiency (\%)	&	$\eta_{cycle}$	&	Data	&	Data	\\
    Alternator Power (W)	&	$\dot{W}_{A}$	&	Data	&	Data	\\
    PC Heat Transfer	&	$\dot{Q}_{PC}$	&	Data	&	Data	\\
    MC Power (W)	&	$\dot{W}_{MC}$	&	Data	&	Data	\\
    RC Power (W)	&	$\dot{W}_{RC}$	&	Data	&	Data	\\
    Turbine Power (W)	&	$\dot{W}_{T}$	&	Data	&	Data	\\
    MC Mass Flow Fraction (-)	&	$y_{1}$	&	Data	&	Data	\\
    LTR UA Value (W/K)	&	$UA_{LTR}$	&	Data	&	Data	\\
    LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	Data	&	Data	\\
    LTR Heat Transfer Rate (W)	&	$\dot{Q}_{LTR}$	&	Data	&	Data	\\
    LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	Data	&	Data	\\
    HTR UA Value (W/K)	&	$UA_{HTR}$	&	Data	&	Data	\\
    HTR Capacitance Ratio (-)	&	$CR_{HTR}$	&	Data	&	Data	\\
    HTR Heat Transfer Rate (W)	&	$\dot{Q}_{HTR}$	&	Data	&	Data	\\
    HTR Effectiveness (-)	&	$\varepsilon_{HTR}$	&	Data	&	Data	\\
    \bottomrule
    \end{tabular}\\
\end{specialtable}

@@

\subsubsection{C-1HTR1T-ON}
%--------------------------------------------------------------------------------------

@@

\subsubsection{C-2HTR3T-ON}
%--------------------------------------------------------------------------------------

@@

\subsection{Thermal Energy Storage Charging Techniques}
%======================================================================================

\subsubsection{C-LFR-PRE}
%--------------------------------------------------------------------------------------

@@

\subsubsection{C-LFR-POST}
%--------------------------------------------------------------------------------------

\subsubsection{C-LFR-PAR}
%--------------------------------------------------------------------------------------

@@

\subsubsection{C-LFR-CIRC}
%--------------------------------------------------------------------------------------

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{how to use}

@@

%Completed suggestions from Ben:

%-I would include the naming scheme upfront and give a table (C-LFR-ON etc.)

%-Here you need to explain what a conventional CSP cycle looks like (briefly). I.e. CSP charges salt, it can discharge when you want it to. Now with our configuration we introduce a 'new' charging mode where heat comes in from the SALT HX as well as from the sun, via the sCO2 Brayton as you say

%-Explain why there is no charging and discharging at same time - because if there is electricity demand heat from LFR would be dispatched direclty rather than thru the SALT HX

%-SALT HX could perhaps be better named sCO2-to-Salt or C2S for short perhaps! Np if you dont want to change it at this late stage

%Completed suggestions from Mike:
